---
title: "Introduction to legcoplus"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`legcoplus` is an R package to reorganise and present data from the Hong Kong Legislative Council (LegCo)
APIs in a more useable manner. It provides functions that restructure data from multiple API requests to 
enhance the efficiency of the use of LegCo's APIs.

It requires the package [`legco`]("https://elgarteo.ga/legco/) to fetch LegCo's open data.

## Prerequiste: Installing legco

### From GitHub

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("elgarteo/legco")
```

### From web

```{r, eval = FALSE}
install.packages("https://elgarteo.ga/legco/legco_0.0.9999.tar.gz", repos = NULL, type="source")
```

## Installing legcoplus

### From GitHub

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("elgarteo/legcoplus")
```

### From web

```{r, eval = FALSE}
install.packages("https://elgarteo.ga/legco/legcoplus/legcoplus_0.0.9999.tar.gz", repos = NULL, type="source")
```

### Load legcoplus

```{r}
library(legcoplus)
```

## Using legcoplus

### List of Functions

The package contains the following functions:

* `all_members()` searches everyone who speaks in LegCo with unique identifiers from different LegCo APIs'
databases.
* `answered_questions()` fetches more detailed information and the full text of questions put on the government
by any given LegCo member.
* `division_date()` searches all division(s) held in LegCo Council and committee meetings on any given date.
* `member_voting_record()` returns the voting record in LegCo Council and committee meetings of any given
LegCo member.

All functions can also be accessed with the prefix `legco_`, e.g. `legco_all_members()` and `all_members()`
return the same result.

### Examples

The unique identifiers of different LegCo databases are not interchangeable. The most notable exmaple is 
`'MemberID'`